Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-15 write-ups/PLDI/paper.tex
Add discussion on performance

\paragraph{Results}

@@

>>>>

\paragraph{Responsiveness}

@@

\paragraph{Performance}
\myfig~\ref{fig:} reports the overhead brought by the scheduling of
non-cooperative kernels over the cooperative kernel execution time
(geometric mean over all experiences), along with the period at which
non-cooperative kernels can be scheduled. Non-cooperative kernels
running on a single workgroup lead to almost no overhead, but the period
is far too high to meet the needs of graphics workloads. As more
workgroups are dedicated to non-cooperative kernels, they execute
quickly enough to be scheduled at the expected period. Yet, as expected,
this increase the execution time overhead of the cooperative
kernel. Still, in average heavy workloads meet their period for an
overhead less than 1.4, which we consider reasonable, while light and
medium workloads meet their period with only a very light overhead on
the cooperative kernel.
